Nirdizati: A Web-based Tool for Predictive Process Monitoring

### 2017-06-12 BPM17-demo-paper/paper.tex
add skeleton

\section{Architectural Overview} \label{sec:arch}

\section{User Interface} \label{sec:UI}

\section{Conclusion} \label{sec:conclusion}

\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

\section{Nirdizati Training} \label{sec:training}
First, we have the Front-end application which acts as the interface for the user to
select settings used for prediction and to analyze the prediction results. The second
module is the Log Manager which is responsible for managing the logs. Uploading
and retrieving the logs are the basic operations of this module. The third module is
the Encoder which retrieves the log from the storage, parses it and prepares the log for
the training phase in the Predictive Module. In this part, we retrieve the encoded data,
split it into training and test set for evaluation, and build the predictive model from the
training data. Finally, using the test data, we test it against the model created to get its
accuracy. The aggregation of the results are done in the Evaluation Module which is
tasked to calculate the error of the prediction model created.

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-training-architecture}
	\caption{A high-level overview of Nirdizati Training.}
	\label{fig:RNNexample}
\end{figure}
%\vspace{-\baselineskip}

\section{Nirdizati Runtime} \label{sec:runtime}
Figure~\ref{fig:dfd_0} illustrates the flow of data through the proposed system. A workflow management system (WFMS) continuously registers tasks performed in the organization.
This serves as an input to our system, in the form of a stream of events.
Next, the produced stream is consumed by a web server which is responsible for storing data and further information processing. 
Web server, in turn, communicates with a predictive engine which applies pre-trained models for a business process and returns all the results of calculations.
After web server receives the outputs from each predictive model, it writes them to a database and updates corresponding clients.
From the user's side, the results are visualized via a dashboard-based interface which is capable of sending queries requesting various visualization options.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{img/dfd_0}
	\caption{High-level data flow diagram in a Yourdon-Coad notation}
	\label{fig:dfd_0}
\end{figure}

Based on this data flow diagram, we devise the main parts and high-level components of the system (Figure~\ref{fig:arch}):

\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\item streaming platform
	\item web server with load balancer and internal components
	\item predictive engine
	\item client-side user interfaces
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{img/nirdizati-runtime-architecture}
	\caption{Proposed system design architecture}
	\label{fig:arch}
	%	\vspace{-5\baselineskip}
\end{figure}

Process workers and operational managers – typical users of such system – can set the process performance targets and subscribe to a stream of warnings and alerts generated whenever these targets are predicted to be violated. Thus, process workers will be capable of making more informed, data-driven decisions to get a better control of the process execution. This is especially beneficial for processes where process workers have more leeway to make corrective actions, for example, in a lead management process.

\section{Conclusion} \label{sec:conclusion}
The source code has been released as open source software under the Lesser GNU Public License (L-GPL) at \url{http://github.com/nirdizati}. The developed engine has been deployed on the server belonging to the Institute of Computer Science and can be accessed at \url{http://nirdizati.com}.
\bibliographystyle{splncs03}
\bibliography{paper}
